\section{Tier T1: Linear Autonomous Semigroup Case}

\subsection{Problem statement}
Determine when an autonomous linear generator supports a persistent subsystem decomposition whose finite-horizon leakage is controlled by slow-carrier deformation and weak reduced coupling.

\subsection{Assumptions}
\begin{enumerate}
\item $L \in \mathbb{C}^{n \times n}$ generates $\dot x = Lx$.
\item A slow spectral set $\sigma_s(L)$ is separated from the remaining spectrum by gap $\delta > 0$.
\item The identified carrier projector $P$ approximates the Riesz projector $P_\star$ with
\[
\varepsilon_s := \|P - P_\star\|_2.
\]
\item In an orthonormal carrier basis $V$, the reduced operator satisfies
\[
A = V^\ast L V = D + R,
\qquad
\rho := \|R\|_2,
\]
with $D$ block diagonal in the proposed subsystem partition.
\end{enumerate}

\subsection{Expected statement}
For carrier-restricted data and finite horizons before repeated transfer saturates,
\[
\ell(t) \le C_1 \varepsilon_s + C_2 M(t)^2 \rho t + C_3 (\rho t)^2,
\]
where $M(t)$ controls semigroup growth on the reduced dynamics. In stable normal or mildly nonnormal settings, this reduces to the affine leading-order law
\[
\ell(t) \lesssim \varepsilon_s + \rho t.
\]

\subsection{Proof ingredients}
\begin{enumerate}
\item Riesz projector calculus and gap-based subspace perturbation bounds.
\item A Duhamel expansion for $e^{t(D+R)} - e^{tD}$.
\item Stability estimates linking carrier mismatch to observed leakage.
\item Reduced-model block residual control.
\end{enumerate}

\subsection{Obstruction list}
\begin{enumerate}
\item Vanishing gap or clustered slow/fast spectrum.
\item Poorly conditioned eigenvectors or severe nonnormality.
\item Block residuals large enough that $\rho t$ is not perturbative.
\end{enumerate}

\subsection{Correspondence to numerics}
Numerical corroboration is currently implemented on `BP_Linear_Two_Block` and `BP_Nearly_Decomposable_Chain` via spectral gap extraction, projector deformation, reduced residuals, leakage trajectories, and horizon comparison.

\subsection{Current confidence level}
High confidence for finite-dimensional autonomous reference families; medium confidence for broad generality statements beyond the implemented assumptions.

\subsection{Open proof gaps}
The current note does not prove sharp constants, does not cover strong nonnormality, and does not package a single theorem spanning all Markov and nonnormal edge cases.
