\section{Tier T5: Stochastic Systems}

\subsection{Problem statement}
Translate subsystem emergence diagnostics into a stochastic setting where the relevant objects are propagators, generators, metastable decompositions, and uncertainty bounds.

\subsection{Assumptions}
\begin{enumerate}
\item A Markov semigroup or transition operator is available or estimable.
\item Slow modes correspond to metastable or low-lying spectral structure.
\item Sampling uncertainty is tracked explicitly.
\end{enumerate}

\subsection{Expected statement}
Only a probabilistic or expectation-level statement is targeted:
\[
\mathbb{E}[\ell(t)] \le C_1 \varepsilon_s + C_2 \rho t + \text{higher-order terms},
\]
with autonomy horizon replaced by a confidence-bounded random quantity.

\subsection{Proof ingredients}
\begin{enumerate}
\item Perturbation of stochastic propagators or generators.
\item Concentration or bootstrap control for estimated leakage.
\item Metastable decomposition consistency.
\end{enumerate}

\subsection{Obstruction list}
\begin{enumerate}
\item Insufficient sampling.
\item Model misspecification in the estimated propagator.
\item State aggregation that creates artificial metastability.
\end{enumerate}

\subsection{Correspondence to numerics}
`BP_Noisy_Metastable_Network` remains the accepted stochastic reference, while `BP_T5_Stochastic_Stress_Pair` adds a matched-versus-sample-stress comparison that reports bootstrap width, estimation error proxies, and confidence-bounded horizons under the same metastable transition structure.

\subsection{Current confidence level}
Medium confidence on the implemented stochastic protocol; low confidence on a general theorem without stronger concentration assumptions.

\subsection{Open proof gaps}
The current note does not prove finite-sample concentration rates or a theorem covering both continuous-time diffusions and discrete-state networks in one package. The new stress pair is bounded protocol evidence for uncertainty sensitivity, not a finite-sample concentration theorem.
